Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-12 RR_manuscript/Draft_RR.Rmd
edits

The mean of the number of different predictors included in teams' models was `r round(predictor_n$mean_predictor,1)` (defined as variables or columns in the data table).
This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `r round(predictor_n$min_predictor,1)`-`r `round(predictor_n$max_predictor,1)`).
Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.

@@

Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored. 
Crowd-sourcing is limited by the sampled analysts and their biases.
Multiverse analyses are limited even further by the group of researchers who define possible analytic pathways.
Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e. in the present case how communicative pressures of certain functions are expressed in the acoustic signal. 
Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].

@@

See <https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png>.

>>>>

The mean of the number of different predictors included in teams' models was `r round(predictor_n$mean_predictor,1)` (defined as variables or columns in the data table).
This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `r round(predictor_n$min_predictor,1)- round(predictor_n$max_predictor,1)`).
Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.

@@

Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored. 
Crowd-sourcing is limited by the sampled analysts and their biases.
Multiverse analyses are limited even further by the group of researchers who define possible analytic pathways.
Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e. in the present case how communicative pressures of certain functions are expressed in the acoustic signal. 
Possible tools to strengthen theoretical development are related to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].

@@

See <https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy-all.png>.
